Comparing Power Optimizations in the Reorder Buffer

### 2011-06-10 paper/end.tex
Results for distributed buffers.

For the FP heavy stream, we saw essentially no advantages using the dynamic approach, due to our modeled processor having only one FP functional unit clogging the buffer. With the other two streams, we saw dramatic improvement in power savings from the dynamic buffer, in the form of saved bit cycles.

>>>>

For the FP heavy stream, we saw essentially no advantages using the dynamic approach, due to our modeled processor having only one FP functional unit clogging the buffer. With the other two streams, we saw dramatic improvement in power savings from the dynamic buffer, in the form of saved bit cycles. It is observed that the optimized ROB is a bit more performance minded than the regular dynamic ROB, averaging more bits per cycle and less cycles to complete. In the integer heavy set, this combination yielded a 2.2\% increase in bit-cycles for the optimized dynamic buffer, while in the mixed stream the difference in cycles pushed the optimized dynamic ROB's bit-cycles to be 2.8\% better than the non-optimized case.
